Temporal semantics for a live coding language

### 2014-05-07 paper/paper.tex
small tweaks to early figure

@@

\authorinfo{Sam Aaron}{}{}
\authorinfo{Dominic Orchard}{}{}
\title{A programming model for temporal coordination (in music)}

@@

@@

\begin{figure}[t]
\subfigure[Three chord program in \lang{}]{
\begin{minipage}{0.46\linewidth}
\[
\hspace{-6em}
\begin{array}{l}
\play C \\
\play E \\ 
\play G \\
\sleep 1 \\
\play F \\
\play A \\
\play C \\
\sleep 0.5 \\
\play G \\
\play B \\
\play D \\
\end{array}
\]
\end{minipage}
\label{three-chord-example}
}
\subfigure[Timing of the three chord program]{
\begin{minipage}{0.46\linewidth}
\note{insert nice diagram that shows when the notes
occur over the 1.5s duration} \\
\end{minipage}
\label{three-chord-timing}
}
\caption{Playing three chords (C major, F major, G major) 
in \lang{} with the second two chords played
closer together by $0.5s$.}
\end{figure}

>>>>

\CustomVerbatimEnvironment{SVerbatim}{Verbatim}{fontsize=\footnotesize,xleftmargin=0.5cm,xrightmargin=0.5cm,framesep=3mm,commandchars=\\\{\}}

@@

\authorinfo{Sam Aaron}{}{}
\authorinfo{Dominic Orchard}{}{}
\title{Temporal semantics for a live coding language} 
% A programming model for temporal coordination (in music)}

@@

\begin{abstract}
Sonic Pi is a music live coding language that has been designed for
educational use, as a first programming language. However, it is
not straightforward to achieve the necessary simplicity of a first language
in a music live coding setting, for reasons largely related to the
manipulation of time. The original version of Sonic Pi used a 'sleep'
function for managing time. However, whilst this approach was conceptually
simple, it resulted in badly timed music - especially when multiple musical
threads were executing concurrently. This paper describes an alternative
programming approach for timing (implemented in Sonic Pi v2.0) which
maintains syntactic compatibility with version 1, yet provides accurate
timing via specific interaction between real time and a "virtual time".
We provide a formal specification of the temporal behaviour of Sonic Pi,
motivated in relation to other recent approaches to the semantics of time in
live coding and general computation. We then define a monadic model of the
Sonic Pi temporal semantics which is sound with respect to this
specification, using Haskell as a metalanguage. 
\end{abstract}

@@

\begin{SaveVerbatim}{example1}
play C
play E
play G
sleep 1
play F
play A
play C
sleep 0.5
play G
play B
play D
\end{SaveVerbatim}

\begin{figure}[t]
\subfigure[Three chord program in \lang{}]{
\begin{minipage}{0.46\linewidth}
%\[
%\hspace{-6em}
%\begin{array}{l}
%\play C \\
%\play E \\ 
%\play G \\
%\sleep 1 \\
%\play F \\
%\play A \\
%\play C \\
%\sleep 0.5 \\
%\play G \\
%\play B \\
%\play D \\
%\end{array}
%\]
\BUseVerbatim[fontsize=\footnotesize,baselinestretch=0.97]{example1} \\
\end{minipage}
\label{three-chord-example}
}
\subfigure[Timing of the three chord program]{
\begin{minipage}{0.46\linewidth}
\note{insert nice diagram that shows when the notes
occur over the 1.5s duration} \\
\end{minipage}
\label{three-chord-timing}
}
\caption{Playing three chords (C major, F major, G major) 
in \lang{} with the second two chords played
closer together by $0.5s$.}
\end{figure}
